---
title: "R Notebook"
output: html_notebook
---

# Running WGCNA for clustering
WGCNA is a powerful method to detect groups of coexpressed genes and reveal temporal patterns in our data.
Using [this](https://www.bioconductor.org/packages/release/bioc/vignettes/CVE/inst/doc/WGCNA_from_TCGA_RNAseq.html) as a guide.

```{r}
library(WGCNA)
Annotated_Rlog_Positive_Averages <- read.csv("~/local_git/NC_Timecourse/RNA-Seq/Exports/Annotated_Rlog_Positive_Averages.csv", row.names=1, stringsAsFactors=FALSE)
rownames(Annotated_Rlog_Positive_Averages) <- Annotated_Rlog_Positive_Averages$Chick_ENSEMBL

ddsTC_Condition_WE_vc_NC_All <- read.csv("./Exports/ddsTC_Condition_WE_vc_NC_All.csv", stringsAsFactors=FALSE)
Conition_Enriched <- subset(ddsTC_Condition_WE_vc_NC_All, padj < 0.05, log2FoldChange > 0.5)

WGCNA_matrix <- t(Annotated_Rlog_Positive_Averages[Conition_Enriched$Chick_ENSEMBL,2:7])
s = abs(bicor(WGCNA_matrix))

powers = c(c(1:10), seq(from = 12, to=30, by=2))
sft = pickSoftThreshold(WGCNA_matrix, powerVector = powers, verbose = 5)
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab='Soft Threshold (power)',ylab='Scale Free Topology Model Fit,signed R^2',
     type='n', main = paste('Scale independence'));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=1,col='red'); abline(h=0.90,col='red')

#calculation of adjacency matrix
beta = 5
a = s^beta
#dissimilarity measure
w = 1-a

#create gene tree by average linkage hierarchical clustering 
geneTree = hclust(as.dist(w), method = 'average')

#module identification using dynamic tree cut algorithm
modules = cutreeDynamic(dendro = geneTree, distM = w, deepSplit = 4, pamRespectsDendro = FALSE,
                            minClusterSize = 50)
#assign module colours
module.colours = labels2colors(modules)

#plot the dendrogram and corresponding colour bars underneath
plotDendroAndColors(geneTree, module.colours, 'Module colours', dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05, main='')

#set a threhold for merging modules. In this example we are not merging so MEDissThres=0.0
MEDissThres = 0.25
merge = mergeCloseModules(WGCNA_matrix, module.colours, cutHeight= MEDissThres, verbose =3)
mergedColors = merge$colors
mergedMEs = merge$newMEs

plotDendroAndColors(geneTree, cbind(module.colours, mergedColors), c("Dynamic Tree Cut", "Merged dynamic"), dendroLabels= FALSE, hang=0.03, addGuide= TRUE, guideHang=0.05)

moduleColors = mergedColors
colorOrder = c("grey", standardColors(50))
moduleLabels = match(moduleColors, colorOrder)-1
MEs = mergedMEs
colors <- colorRampPalette(c("#0584bc","#FFFFFF", "#e45649"))(250)

pheatmap::pheatmap(MEs, cluster_rows = F, color = colors,
                   filename = "./Exports/WGCNA_Sample_Color_Heatmap.pdf")

# So we get a good idea of which modules are active in each stage.
names(mergedColors) <- Annotated_Rlog_Positive_Averages[Conition_Enriched$Chick_ENSEMBL,1]

```

We can also check out how these clusters look in a line graph. Might be better.

```{r}
MEs
```


## Looking at GO In these different modules.

```{r}
library(clusterProfiler)
library(org.Hs.eg.db)
library(viridis)
library(ggplot2)
data <- Annotated_Rlog_Positive_Averages[names(mergedColors),c(1,8:11)]
data$Group <- mergedColors
summary(as.factor(data$Group))
write.csv(data, file = "Exports/WGCNA_Gene_Modules.csv")

GO_Results <- compareCluster(Human_Entrezid~Group, fun = "enrichGO", data = data, ont = "BP", qvalueCutoff = 0.05, readable = T,
                             OrgDb = org.Hs.eg.db)

GO_Results.simplify <-simplify(GO_Results)

dotplot(GO_Results.simplify, title = "WGCNA BP Enrichment") + scale_color_viridis(direction=-1)
ggsave(file = "./Exports/WGCNA_BP_Enrichment.pdf", width = 12, height = 8)

```

This has the power to identify new genes involved in different aspects of NC development.
For example, let's look at the genes in the 'greenyellow' module, which seem to be related to muscle development.

```{r}
greenyellow <- data[data$Group == "greenyellow",]
greenyellow[greenyellow$TF_Status == "Transcription Factor", 2]
```
In this case, we see well-known NC transcription factors like TFAP2B, MSX1, and FOXD3 having similar signatures to muscle transcription factors like NKX2-6 and TBX20. This may indicate that these other transcription factors act in NC destined for muscle development.
